Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach

### 2021-02-27 0_manuscript_blind/itt-emotion_blind_V6-6.tex
Getting everything ready for sending off

        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
                Hirofumi Nonaka                                                 \protect\affmark[1] \and
                Toru Hiraoka                                                    \protect\affmark[2]
        }

        \authorrunning{E. Alemán Carreón et al.}

        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com}, 
                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
                \and
                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
                    \hspace*{1em} \email{mendoza.espana@gmail.com}
                \and
                    \hspace*{1em} Hirofumi Nonaka \at
                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
                \and
                    \hspace*{1em} Toru Hiraoka \at
                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
                \and
                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
                \and
                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
        }

@@

  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation. We would like to show gratitude to Mr. Liangyuan Zhou, Ms. Min Fan, and Ms. Eerdengqiqige for this.

  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.

  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).

  Conflict of interest: none

>>>>

        \author{REDACTED}

        \authorrunning{REDACTED}

        \institute{REDACTED}

@@

  REDACTED
